Towards Comparable Active Learning

### 2023-06-08 doc/al_benchmark_paper.tex
paper update

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Oracle}\label{sec:oracle}
\begin{minipage}{0.5\linewidth}
	Posing Active Learning as a combinatorial problem, the oracle set $\mathcal{U}_b$ for a given dataset, model and training procedure is the set that induces the highest AUC score for a given budget.
	However, since this problem is not solvable for realistic datasets, previous works have proposed approximations to this oracle sequence. 
	\cite{zhou2021towards} has used simulated annealing to search for the optimal subset and used the best  solution found after a fixed time budget. 
	Even though their reported performance curves display a significant lift over all other acquisition functions, we found the computational cost of reproducing this oracle for all our datasets to be prohibitive (The authors reported the search to take several days per dataset on 8 V100 GPUs).
	In this paper we propose a greedy oracle algorithm that constructs an approximation of the optimal set in an iterative fashion.
\end{minipage}
\hspace{2mm}
\begin{minipage}{0.45\linewidth}
	\begin{algorithm}[H]
		\caption{Oracle}\label{alg:oracle}
		\begin{algorithmic}[1]
			\Require $\mathcal{U}, \mathcal{L}, \mathcal{Y}, \mathcal{D}_\text{test}$ Train, Margin, $\tau, \hat y_\theta$ 
			\State $\text{acc} \gets \operatorname{Train}(\mathcal{L}, \mathcal{D}_\text{test}, \hat y_\theta)$ 
			%\State $u \underset{\tau}{\sim} \text{unif}(1:|\mathcal{U}|)$
			\State $r^* \gets 0$
			\For{$k := 1 \ldots \tau$}
			\State $\mathcal{L}' \gets \mathcal{L}^{(i)} \cup \{(u_k, A(u_k))\}$
			\State $\text{acc}' \gets \operatorname{Train}(\mathcal{L}', \mathcal{D}_\text{test}, \hat y_\theta)$  
			\State $r \gets \text{acc} - \text{acc}'$
			\If{$r > r^*$} 
			\State $r^* \gets r$
			\State $u^* \gets u_k$
			\EndIf
			\EndFor
			\If{$r^* = 0$}
			\State $u^* \gets \operatorname{margin}(\mathcal{U}, \hat y_\theta)$
			\EndIf
			\Return $u^*$
		\end{algorithmic}
	\end{algorithm}
\end{minipage} \\ [1mm]
Our oracle simply evaluates every data point $u_k = \operatorname{unif(\mathcal{U} | k = 1 \ldots \tau)}$ in a subsample of unlabeled points by fitting the classifier $\hat y$ on $\mathcal{L}^{(i)} \cup u_k$ and directly measuring the resulting test performance.
The data point with the best test performance is selected and added to the labeled pool for that iteration.
We noticed that this oracle is overfitting on the test set, resulting in stagnating or even decreasing performance curves in later AL iterations.
This can happen for example, if the oracle picked a labeled set that enables the classifier to correctly classifier a big portion of easy samples in the test set, but now fails to find the next single unlabeled point that would enable the classifier to succeed on one of the hard samples in the test set.
This leads to a situation, where the selected data point is basically random.\\
To circumvent this problem, we introduced margin sampling \cite{wang2014new} as a fallback option for the oracle.
Whenever the oracle does not find an unlabeled point that results in an increase in performance, it defaults to margin sampling in that iteration.
The resulting greedy algorithm constructs an approximation of the optimal labeled set that consistently outperforms all other algorithms by a significant margin, while requiring relatively low computational cost (scaling linearly in $\tau$).
The pseudocode for our oracle can be found in Alg. \ref{alg:oracle}.
In the algorithm $\operatorname{Train}(\LL, \D_\text{test}, \hat y_\theta)$ trains the classification model $\hat y_\theta$ and returns it's accuracy  on $\D_\text{test}$. \\
Alg. \ref{alg:oracle} replaces the acquisition function in the AL process.

@@

\section{All Results}\label{app:all_results}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.49\linewidth]{img/eval_splice}
	\includegraphics[width=0.49\linewidth]{img/eval_splice_enc} \\ [2mm]
	\includegraphics[width=0.49\linewidth]{img/micro_splice.jpg}
	\includegraphics[width=0.49\linewidth]{img/micro_splice_enc.jpg} \\ [4mm]
\end{figure}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.49\linewidth]{img/eval_dna}
	\includegraphics[width=0.49\linewidth]{img/eval_dna_enc} \\ [2mm]
	\includegraphics[width=0.49\linewidth]{img/micro_dna.jpg}
	\includegraphics[width=0.49\linewidth]{img/micro_dna_enc.jpg} \\ [4mm]
\end{figure}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.49\linewidth]{img/eval_usps}
	\includegraphics[width=0.49\linewidth]{img/eval_usps_enc} \\ [2mm]
	\includegraphics[width=0.49\linewidth]{img/micro_usps.jpg}
	\includegraphics[width=0.49\linewidth]{img/micro_usps_enc.jpg} \\ [4mm]
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.49\linewidth]{img/eval_cifar10}
\includegraphics[width=0.49\linewidth]{img/eval_cifar10_enc} \\ [2mm]
\includegraphics[width=0.49\linewidth]{img/micro_cifar10.jpg}
\includegraphics[width=0.49\linewidth]{img/micro_cifar10_enc.jpg} \\ [4mm]
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.49\linewidth]{img/eval_fmnist}
\includegraphics[width=0.49\linewidth]{img/eval_fmnist_enc} \\ [2mm]
\includegraphics[width=0.49\linewidth]{img/micro_fmnist.jpg}
\includegraphics[width=0.49\linewidth]{img/micro_fmnist_enc.jpg} \\ [4mm]
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.49\linewidth]{img/eval_topv2}
\includegraphics[width=0.49\linewidth]{img/eval_news} \\ [2mm]
\includegraphics[width=0.49\linewidth]{img/micro_topv2.jpg}
\includegraphics[width=0.49\linewidth]{img/micro_news.jpg} \\ [4mm]
\end{figure}

@@

\section{Hyperparameters per AL Algorithm}\label{app:agent_hyperparameters}
\begin{table}[H]
	TODO
\end{table}

\section{Hyperparameters per Dataset}\label{app:hyperparameters}
\begin{table}[H]
	\centering
	\begin{tabular}{l || l | l l l l}
		Dataset & Classifier & Optimizer & LR & Weight Decay & Dropout \\
		\hline
		Splice & [24, 12] & NAdam & 1.2e-3 & 5.9e-5 & 0 \\
		SpliceEnc. & linear & NAdam & 6.2e-4 & 5.9e-6 & 0 \\
		DNA & [24, 12] & NAdam & 3.9e-2 & 3.6e-5 & 0 \\
		DNAEnc & linear & NAdam & 1.6e-3 & 4e-4 & 0 \\
		USPS & [24, 12] & Adam & 8.1e-3 & 1.5e-6 & 0 \\
		USPS & linear & NAdam & 7.8e-3 & 1.9e-6 & 0 \\
		FashionMnist & ResNet18 & NAdam & 1e-3 & 0 & 0 \\
		FashionMnistEnc & linear & Adam & 1.6e-3 & 1e-5 & 5e-2 \\
		Cifar10 & ResNet18 & NAdam & 1e-3 & 0 & 0 \\
		Cifar10Enc & linear & NAdam & 1.7e-3 & 2.3e-5 & 0 \\
		TopV2 & BiLSTM & NAdam & 1.5e-3 & 1.7e-7 & 5e-2 \\
		News & BiLSTM & NAdam & 1.5e-3 & 1.7e-7 & 5e-2 \\
	\end{tabular}
	\caption{Classifier architectures and optimized hyperparameters per dataset. Numbers in brackets signify a MLP with corresponding hidden layers.}
	\label{tab:architectures}
\end{table}

\section{Comparison of Different Classifier Sizes}\label{app:classifier_size}
We tested two different classifier sizes in Splice and DNA:
\begin{itemize}
	\item Small: [24, 12] (2400 parameters)
	\item Big: [24, 48, 48] (5700 parameters)
\end{itemize}
\begin{figure}
	\centering
	\includegraphics[width=0.49\linewidth]{img/supp_dna_small.png}
	\includegraphics[width=0.49\linewidth]{img/supp_dna_big.png}
	\includegraphics[width=0.49\linewidth]{img/supp_micro_dna_small.png}
	\includegraphics[width=0.49\linewidth]{img/supp_micro_dna_big.png}
	\caption{Comparison of small and big classifiers for the DNA dataset}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.49\linewidth]{img/supp_splice_small.png}
	\includegraphics[width=0.49\linewidth]{img/supp_splice_big.png}
	\includegraphics[width=0.49\linewidth]{img/supp_micro_splice_small.png}
	\includegraphics[width=0.49\linewidth]{img/supp_micro_splice_big.png}
	\caption{Comparison of small and big classifiers for the Splice dataset}
\end{figure}

\section{Comparison of different sample sizes}
\begin{figure}[H]
\centering
\includegraphics[width=0.7\linewidth]{img/tau_ablation.png}
\end{figure}

\section{AL Pseudocode}
\begin{algorithm}[H]
	\caption{Active Learning}\label{alg:active_learning}
	\begin{algorithmic}[1]
		\Require $\mathcal{U}$ \Comment{Unlabeled Pool}
		\Require $\tau$ \Comment{Unlabeled Sample Size}
		\Require $\Omega$ \Comment{AL Agent}
		\Require $\omega$ \Comment{Environment State function}
		\State $\mathcal{L}^{(1)} \gets \operatorname{seed}(\mathcal{U})$  \Comment{Create the initial labeled set}
		\State $\mathcal{U}^{(1)} \gets \mathcal{U}$
		\For{$i := 1 \ldots B$}
		\State $\text{acc}^{(i)} \gets \operatorname{Retrain}(\mathcal{L}^{(i)})$  %\Comment{$\operatorname{Retrain}(\mathcal{L}^{(i)})$ is shorthand for $\operatorname{Retrain}(\mathcal{L}^{(i)}, \mathcal{L}^\text{test}, \hat y_\theta, e^\text{max})$}
		%\State $u^{(i)} \sim \text{unif}(1:|\mathcal{U}^{(i)}|)$
		\State $a^{(i)} \gets \Omega(\mathcal{U}^{(i)}) \hspace{1mm};\hspace{2mm} a \in 1:|\mathcal{U}^{(i)}|$ 
		%\Comment{$a^{(i)}$ is an index inside of $u^{(i)}$}
		\State $y^{(i)} \gets \operatorname{label}(\mathcal{U}^{(i)}_{a})$ 
		%\Comment{$u^{(i)}_{a}$ is shorthand for $u^{(i)}_{a^{(i)}}$}
		\State $\mathcal{L}^{(i+1)} \gets \mathcal{L}^{(i)} \cup \{(\mathcal{U}^{(i)}_a, y^{(i)})\}$
		\State $\mathcal{U}^{(i+1)} \gets \mathcal{U}^{(i)} \setminus \{\mathcal{U}^{(i)}_a\}$
		\EndFor
		\State
		\Return $\frac{1}{B} \sum_{i=1}^{B} \text{acc}^{(i)}$
	\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
	\caption{Retrain}\label{alg:retrain}
	\begin{algorithmic}[1]
		\Require $\mathcal{L}$ \Comment{Labeled Pool}
		\Require $\mathcal{D}_\text{val}$ \Comment{Validation Data}
		\Require $\mathcal{D}_\text{test}$ \Comment{Test Data}
		\Require $\hat y_\theta$ \Comment{Class. Model}
		\Require $e^\text{max}$ \Comment{Maximum Epochs}
		\State $\text{loss}^* \gets \infty$
		\For{$i := 1 \ldots e^{\text{max}}$}
		\State $\theta_{i+1} \gets \theta_i - \eta \nabla_\theta \ell(\mathcal{L}, \hat y_{\theta})$
		\State $\text{loss}_i \gets \ell(\mathcal{D}^\text{val}, \hat y_{\theta})$
		\If{$\text{loss}_i < \text{loss}^*$}
		\State $\text{loss}^* \gets \text{loss}_i$
		\Else
		\State Break
		\EndIf
		\EndFor
		\State
		\Return Acc($\mathcal{D}^\text{test}, \hat y_{\theta}$)
	\end{algorithmic}
\end{algorithm}

>>>>

\let\thefootnote\relax\footnotetext{Code available at: \url{https://github.com/wernerth94/comparable-active-learning}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Oracle}\label{sec:oracle}
\begin{minipage}{0.5\linewidth}
	Posing Active Learning as a combinatorial problem, the oracle set $\mathcal{U}_b$ for a given dataset, model and training procedure is the set that induces the highest AUC score for a given budget.
	However, since this problem is not solvable for realistic datasets, previous works have proposed approximations to this oracle sequence. 
	\cite{zhou2021towards} has used simulated annealing to search for the optimal subset and used the best  solution found after a fixed time budget. 
	Even though their reported performance curves display a significant lift over all other acquisition functions, we found the computational cost of reproducing this oracle for all our datasets to be prohibitive (The authors reported the search to take several days per dataset on 8 V100 GPUs).
	In this paper we propose a greedy oracle algorithm that constructs an approximation of the optimal set in an iterative fashion.
\end{minipage}
\hspace{2mm}
\begin{minipage}{0.45\linewidth}
	\begin{algorithm}[H]
		\caption{Oracle}\label{alg:oracle}
		\begin{algorithmic}[1]
			\Require $\mathcal{U}, \mathcal{L}, A, \mathcal{D}_\text{test}$ Train, Margin, $\tau, \hat y_\theta$ 
			\State $\text{acc} \gets \operatorname{Train}(\mathcal{L}, \mathcal{D}_\text{test}, \hat y_\theta)$ 
			%\State $u \underset{\tau}{\sim} \text{unif}(1:|\mathcal{U}|)$
			\State $r^* \gets 0$
			\For{$k := 1 \ldots \tau$}
			\State $\mathcal{L}' \gets \mathcal{L}^{(i)} \cup \{(u_k, A(u_k))\}$
			\State $\text{acc}' \gets \operatorname{Train}(\mathcal{L}', \mathcal{D}_\text{test}, \hat y_\theta)$  
			\State $r \gets \text{acc} - \text{acc}'$
			\If{$r > r^*$} 
			\State $r^* \gets r$
			\State $u^* \gets u_k$
			\EndIf
			\EndFor
			\If{$r^* = 0$}
			\State $u^* \gets \operatorname{margin}(\mathcal{U}, \hat y_\theta)$
			\EndIf
			\Return $u^*$
		\end{algorithmic}
	\end{algorithm}
\end{minipage} \\ [1mm]
Our oracle simply evaluates every data point $u_k = \operatorname{unif(\mathcal{U} | k = 1 \ldots \tau)}$ in a subsample of unlabeled points by fitting the classifier $\hat y$ on $\mathcal{L}^{(i)} \cup u_k$ and directly measuring the resulting test performance.
The data point with the best test performance is selected and added to the labeled pool for that iteration.
We noticed that this oracle is overfitting on the test set, resulting in stagnating or even decreasing performance curves in later AL iterations.
This can happen for example, if the oracle picked a labeled set that enables the classifier to correctly classifier a big portion of easy samples in the test set, but now fails to find the next single unlabeled point that would enable the classifier to succeed on one of the hard samples in the test set.
This leads to a situation, where the selected data point is basically random.\\
To circumvent this problem, we introduced margin sampling \cite{wang2014new} as a fallback option for the oracle.
Whenever the oracle does not find an unlabeled point that results in an increase in performance, it defaults to margin sampling in that iteration.
The resulting greedy algorithm constructs an approximation of the optimal labeled set that consistently outperforms all other algorithms by a significant margin, while requiring relatively low computational cost (scaling linearly in $\tau$).
The pseudocode for our oracle can be found in Alg. \ref{alg:oracle}.
In the algorithm $\operatorname{Train}(\LL, \D_\text{test}, \hat y_\theta)$ trains the classification model $\hat y_\theta$ and returns it's accuracy  on $\D_\text{test}$. \\
Alg. \ref{alg:oracle} replaces the acquisition function in the AL process.

@@

\section{All Results}\label{app:all_results}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.4\linewidth]{img/eval_splice}
	\includegraphics[width=0.4\linewidth]{img/eval_splice_enc} \\ [2mm]
	\includegraphics[width=0.3\linewidth]{img/micro_splice.jpg}
	\includegraphics[width=0.3\linewidth]{img/micro_splice_enc.jpg} \\ [4mm]
\end{figure}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.4\linewidth]{img/eval_dna}
	\includegraphics[width=0.4\linewidth]{img/eval_dna_enc} \\ [2mm]
	\includegraphics[width=0.3\linewidth]{img/micro_dna.jpg}
	\includegraphics[width=0.3\linewidth]{img/micro_dna_enc.jpg} \\ [4mm]
\end{figure}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.4\linewidth]{img/eval_usps}
	\includegraphics[width=0.4\linewidth]{img/eval_usps_enc} \\ [2mm]
	\includegraphics[width=0.3\linewidth]{img/micro_usps.jpg}
	\includegraphics[width=0.3\linewidth]{img/micro_usps_enc.jpg} \\ [4mm]
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.4\linewidth]{img/eval_cifar10}
\includegraphics[width=0.4\linewidth]{img/eval_cifar10_enc} \\ [2mm]
\includegraphics[width=0.3\linewidth]{img/micro_cifar10.jpg}
\includegraphics[width=0.3\linewidth]{img/micro_cifar10_enc.jpg} \\ [4mm]
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.4\linewidth]{img/eval_fmnist}
\includegraphics[width=0.4\linewidth]{img/eval_fmnist_enc} \\ [2mm]
\includegraphics[width=0.3\linewidth]{img/micro_fmnist.jpg}
\includegraphics[width=0.3\linewidth]{img/micro_fmnist_enc.jpg} \\ [4mm]
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.4\linewidth]{img/eval_topv2}
\includegraphics[width=0.4\linewidth]{img/eval_news} \\ [2mm]
\includegraphics[width=0.3\linewidth]{img/micro_topv2.jpg}
\includegraphics[width=0.3\linewidth]{img/micro_news.jpg} \\ [4mm]
\end{figure}

@@

\section{Hyperparameters per AL Algorithm}\label{app:agent_hyperparameters}
\begin{table}[H]
	\centering
	\begin{tabular}{l || l | l}
		Algorithm & Sample Size & \\
		\hline
		BADGE & 100 & \\
		BALD & 100 & Dropout Trials: 5 \\
		Coreset & 8000 & \\
		TypiClust & 10000 & Min Cluster Size: 5, Max \# Clusters: 500 \\
		Margin & 8000 & \\
		Entropy & 8000 & \\
	\end{tabular}
\end{table}

\section{Hyperparameters per Dataset}\label{app:hyperparameters}
\begin{table}[H]
	\centering
	\begin{tabular}{l || l l l }
		Dataset & Seed Set & Budget & Val Split \\
		\hline
		Splice & 1 & 400 & 0.2 \\
		SpliceEnc. & 1 & 60 & 0.2 \\
		DNA & 1 & 300 & 0.2 \\
		DNAEnc & 1 & 40 & 0.2 \\
		USPS & 1 & 400 & 0.2 \\
		USPSEnc & 1 & 600 & 0.2 \\
		FashionMnist & 100 & 2000 & 0.04 \\
		FashionMnistEnc & 1 & 500 & 0.04 \\
		Cifar10 & 100 & 2000 & 0.04  \\
		Cifar10Enc & 1 & 350 & 0.04  \\
		TopV2 & 1 & 125 & 0.25  \\
		News & 1 & 1500 & 0.03  \\
	\end{tabular}
	\caption{Size of the seed set is given by number of labeled sample per class.}
	\label{tab:architectures}
\end{table}
\begin{table}[H]
\centering
\begin{tabular}{l || l | l l l l l}
	Dataset & Classifier & Optimizer & LR & Weight Decay & Dropout & Batch Size \\
	\hline
	Splice & [24, 12] & NAdam & 1.2e-3 & 5.9e-5 & 0 & 43 \\
	SpliceEnc. & linear & NAdam & 6.2e-4 & 5.9e-6 & 0 & 64 \\
	DNA & [24, 12] & NAdam & 3.9e-2 & 3.6e-5 & 0 & 64 \\
	DNAEnc & linear & NAdam & 1.6e-3 & 4e-4 & 0 & 64 \\
	USPS & [24, 12] & Adam & 8.1e-3 & 1.5e-6 & 0 & 43 \\
	USPSEnc & linear & NAdam & 7.8e-3 & 1.9e-6 & 0 & 64 \\
	FashionMnist & ResNet18 & NAdam & 1e-3 & 0 & 0 & 64 \\
	FashionMnistEnc & linear & Adam & 1.6e-3 & 1e-5 & 5e-2 & 64 \\
	Cifar10 & ResNet18 & NAdam & 1e-3 & 0 & 0 & 64 \\
	Cifar10Enc & linear & NAdam & 1.7e-3 & 2.3e-5 & 0 & 64 \\
	TopV2 & BiLSTM & NAdam & 1.5e-3 & 1.7e-7 & 5e-2 & 64 \\
	News & BiLSTM & NAdam & 1.5e-3 & 1.7e-7 & 5e-2 & 64 \\
\end{tabular}
\caption{Classifier architectures and optimized hyperparameters per dataset. Numbers in brackets signify a MLP with corresponding hidden layers.}
\label{tab:architectures}
\end{table}

\section{Comparison of Different Classifier Sizes}\label{app:classifier_size}
We tested two different classifier sizes in Splice and DNA:
\begin{itemize}
	\item Small: [24, 12] (2400 parameters)
	\item Big: [24, 48, 48] (5700 parameters)
\end{itemize}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.49\linewidth]{img/supp_dna_small.png}
	\includegraphics[width=0.49\linewidth]{img/supp_dna_big.png}
	\includegraphics[width=0.49\linewidth]{img/supp_micro_dna_small.png}
	\includegraphics[width=0.49\linewidth]{img/supp_micro_dna_big.png}
	\caption{Comparison of small and big classifiers for the DNA dataset}
\end{figure}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.49\linewidth]{img/supp_splice_small.png}
	\includegraphics[width=0.49\linewidth]{img/supp_splice_big.png}
	\includegraphics[width=0.49\linewidth]{img/supp_micro_splice_small.png}
	\includegraphics[width=0.49\linewidth]{img/supp_micro_splice_big.png}
	\caption{Comparison of small and big classifiers for the Splice dataset}
\end{figure}
Even though the ranking between the two sizes of classifier does change, we observed no systematic that would favor one algorithm. 
We therefore rely on the different datasets to provide classifiers of varying size and architecture.

\section{AL Pseudocode}
\begin{algorithm}[H]
	\caption{Active Learning}\label{alg:active_learning}
	\begin{algorithmic}[1]
		\Require $\LL, \U, \D_\text{test}, \operatorname{Train}, \operatorname{Seed}, \hat y$
		\Require $\Omega$ \Comment{Acquisition Function}
		\State $\LL^{(1)} \gets \operatorname{Seed}(\U)$  \Comment{Create the initial labeled set}
		\State $\U^{(1)} \gets \U$
		\For{$i := 1 \ldots B$}
		\State $\text{acc}^{(i)} \gets \operatorname{Train}(\LL^{(i)})$ 
		\State $a^{(i)} \gets \Omega(\mathcal{U}^{(i)})$ 
		\State $\mathcal{L}^{(i+1)} \gets \mathcal{L}^{(i)} \cup \{(\U^{(i)}_a, A(\U^{(i)}_{a}))\}$
		\State $\U^{(i+1)} \gets \U^{(i)} \setminus \{\U^{(i)}_a\}$
		\EndFor
		\State
		\Return $\frac{1}{B} \sum_{i=1}^{B} \text{acc}^{(i)}$
	\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
	\caption{Retrain}\label{alg:retrain}
	\begin{algorithmic}[1]
		\Require $\LL, \D_\text{val}, \D_\text{test}$
		\Require $\hat y, e_\text{max}$
		\State $\text{loss}^* \gets \infty$
		\For{$i := 1 \ldots e^{\text{max}}$}
		\State $\hat y_{i+1} \gets \hat y_i - \eta \nabla_{\hat y} \ell(\mathcal{L}, \hat y)$
		\State $\text{loss}_i \gets \ell(\mathcal{D}^\text{val}, \hat y)$
		\If{$\text{loss}_i < \text{loss}^*$}
		\State $\text{loss}^* \gets \text{loss}_i$
		\Else
		\State Break
		\EndIf
		\EndFor
		\State
		\Return Acc($\mathcal{D}^\text{test}, \hat y$)
	\end{algorithmic}
\end{algorithm}
